### 2011-04-04 msm2aa.tex
Updates.
Updates, etc.

	\subsection{Multiple integrals}

>>>>

	\subsection{Multiple integrals}
		\subsubsection{Single integrals}

		\subsubsection{Geometric interpretation of single integrals}

		\subsubsection{Double integrals}
		\begin{defn}
			The double integral of a continuous function $f(x,y)$ defined on a closed domain $D$ is defined by
			\[
				\iint\limits_D f(x,y) dxdy = \lim_{max|\Delta x_i| \to 0} \lim_{max|\Delta y_j| \to 0} \sum_{j=0}^{m-1} \sum_{i=0}^{n-1} f( \xi_i, \eta_j) \Delta x_i \Delta y_j
			\]
			where
			\[
				\Delta x_i = x_{i+1}- x_i, \quad \Delta y_j = y_{j+1}- y_j, \quad \xi_i \in [x_i, x_{i+1}], \quad \eta_j \in [x_j, x_{j+1}]
			\]
			and the sum for all $(x_i, y_j) \in D$.
		\end{defn}

		\subsubsection{Geometric interpretation of double integrals}

		\subsubsection{Properties of double integrals}
		\begin{enumerate}
			\item If $D$ is a region of $\mathbb{R}^2$, then $\iint\limits_D f(x,y) dxdy$ is the volume of a solid region $S$ lying above domain $D$ in the $xy$-plane and below the surface $z=f(x,y)$.
			\item $\iint\limits_D 1 dxdy = $ area of $R$.
			\item If $S$ is a region of $\mathbb{R}^3$ then $\iiint\limits_S 1 dxdydz = $ volume of $S$.
			\item Suppose $f$ and $g$ are continuous functions, $c$ and $d$ are constants, then
					\[
						\iint\limits_D [ cf(x,y) + dg(x,y)] dxdy = c \iint\limits_D f(x,y) dxdy + d \iint\limits_D g(x,y) dxdy
					\]
			\item Let $D = D_1 \cup D_2$, where $D_1$ and $D_2$ are non-overlapping regions. If $\iint\limits_D f(x,y)$ dxdy exists, then
					\[
						\iint\limits_D f(x,y) dxdy = \iint\limits_{D_1} f(x,y) dxdy + \iint\limits_{D_2} f(x,y) dxdy
					\]
		\end{enumerate}

		\subsubsection{Fubini's theorem}
		\begin{thm}
			Let $f:\mathbb{R}^2 \to \mathbb{R}$ be continuous on $D$, which is given as
			\[
				D = {(x,y): a \leq x \leq b, c(x) \leq y \leq d(x)},
			\]
			where $c(x)$ and $d(x)$ are smooth. If $\iint\limits_D f(x,y) dxdy$ exists, then
			\[
				\iint\limits_D f(x,y) dxdy = \int\limits_a^b \left( \int\limits_{c(x)}^{d(x)} f (x,y) dy \right) dx = \int\limits_a^b dx \int\limits_{c(x)}^{d(x)} f (x,y) dy
			\]
		\end{thm}

		\subsubsection{Geometric interpretation of fubini's theorem}
